Inferring the rate of Earth-like exoplanets from noisy data

### 2014-03-25 document/ms.tex
introduction text

>>>>

STUFF HERE ABOUT EARTH ANALOGS.

This study is novel in a number of ways.
We create probabilistic information about the full exoplanet population
  \emph{not} by weighting the detected objects by the inverse detection efficiency (CITE PETIGURA),
  but rather by forward modeling the observed distribution subject to the detection efficienty.
Re-weighting the data by inverse selection probability---%
  a method called V-max in the quasar and galaxy luminosity function contexts---%
  is not wrong,
  but it produces a higher-variance estimate of the population than a justified likelihood approach.
Here our likelihood function is a Poisson rate likelihood;
  it makes the fundamental assumption that the data points are independently drawn from the model,
  but no other assumptions.
Indeed, the assumptions behind this study are weaker than those of any previous study
  of the Earth-analog population (CITE PETIGURA, DONG).

Another new aspect of this study is that it makes use of very flexible distribution function models.
Indeed most of the models we consider are ``non-parametric'' in the weak sense
  that they have enormous numbers of free parameters
  (not the strong sense of having an \emph{infinite} number of free parameters).
The models are protected from degeneracies and over-fitting by priors.
In some models we assume that the two-dimensional distribution of planets
  in radius and period is separable;
  in others we don't.
We treat all of these parameters as ``nuisance parameters'' when we ask questions
  about the occurrence of Earth analogs.
That is, our rate conclusions are fully marginalized,
  and those marginalizations are over non-trivial numbers of parameters.

When we make conclusions about the radius disribution of exoplanets,
  the distribution parameters are not nuisances but in fact our object.
Even then, however, our results will have the period parameters marginalized out.

Perhaps the most important novelty of this study is in its treatment of errors.
Although planet periods are usually precisely measured,
  planet radius measurements near Earth radius have large uncertainties.
The justified probabilistic approach to including these uncertainties in a distribution analysis
  is to introduce the ``true'' radii as latent variables and infer and marginalize them out
  along with all other nuisance parameters.
Although this sounds expensive---and it can be---%
  there is a simple approach we have been advocating (CITE HOGG) that makes use of importance sampling.
We use this approach here;
  our results are fully marginalized over posterior uncertainties in all of the planet radii.
More will be said about this below;
  the importance sampling looks like a product over data points
  of sums (averages) over individual-datum radius samplings.
